Box

### 2021-07-13 MS/box.Rmd
Just reorganised section of box to make flow better. First gcrack at temperature corrected SMD.

## *BOX 1: Example of how to derive sampling variance*

Here we show how to obtain sampling variance for a slope (or a 'rate of change') when you are given measurements of a physiological trait at two points in an environmental gradient (e.g. temperature, salinity, acidity). We also go on to derive sampling variance for the difference between two slopes so that we can use powerful meta-analytic models using this effect size.

@@

ARR assumes that the units for the mean difference across studies is consistent. This will often not be the case for many meta-analyses that hope to synthesise a wide diversity of trait types that vary in their units (e.g., ul/g, grams, seconds, minutes). Fortunately, $lnRR$ and SMD (Table 1) already control for unitary differences. As such, we can apply some of the same logic we discuss above to SMD, to correct for both temperature differences. Table 1 provides the formula for SMD, it's pooled standard deviation, and sampling variance. We won't re-iterate these formulas again. Just like with ARR we can apply our temperature correction to the SMD formula as follows:

$$
SMD_{T} = \frac{\left(\bar{X}_{2} - \bar{X}_{1}\right)}{SD_{p}\left( T_{2} - T_{1}\right)}J
$$
Here, we can see that the difference between $X_1$ and $X_2$ is standardised by the pooled SD, essentially correcting for unitary differences. Dividing SMD by the temperature difference on top of that results in correcting the effect size further by temperature. To derive the sampling variance for $SMD_T$ we can apply the same principles as we did above to derive an approximate sampling variance as:

$$
s_{SMD_{T}}^2 = \left(\frac{1}{{T_{2} - T_{1}}}\right)^2 +  \frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)}
$$
### Sampling variance for the difference between two slopes

@@

>>>>

## *BOX 1: Examples of how to derive sampling variances*

Here we show how to obtain sampling variance for a slope (or a 'rate of change') when you are given measurements of a physiological trait at two points in an environmental gradient (e.g. temperature, salinity, acidity). We also go on to derive sampling variance for the difference between two slopes, and finally end on showing how SMD can be corrected to account for both unitary and temperature differences across effect sizes. The sampling variances associated with these 'new' effect sizes will allow one to take advantage of powerful meta-analytic models.

@@

### Sampling variance for the difference between two slopes

@@

ARR assumes that the units for the mean difference across studies is consistent. This will often not be the case for many meta-analyses that hope to synthesise a wide diversity of trait types that vary in their units (e.g., ul/g, grams, seconds, minutes). Fortunately, $lnRR$ and SMD (Table 1) already control for unitary differences. As such, we can apply some of the same logic we discuss above to SMD to correct for both temperature and unitary differences. Table 1 provides the formula for SMD, it's pooled standard deviation, and sampling variance. We won't re-iterate these formulas again. Just like with ARR we can apply our temperature correction to the SMD formula as follows:

$$
SMD_{T} = \frac{\left(\bar{X}_{1} - \bar{X}_{2}\right)}{SD_{p}\left( T_{2} - T_{1}\right)}J
$$

Here, we can see that the difference between $X_1$ and $X_2$ is standardised by the pooled SD, essentially correcting for unitary differences. Dividing SMD by the temperature difference on top of that results in correcting the effect size further by temperature. To derive the sampling variance for $SMD_T$ we can apply the same principles as we did above to derive an approximate sampling variance as:

$$
s_{SMD_{T}}^2 = \left(\frac{1}{{T_{2} - T_{1}}}\right)^2 +  \frac{N_{1} + N_{2}}{N_{1}N_{2}}  + \frac{SMD_{T}^2}{2\left( N_{1} + N_{2}\right)}
$$
